---
title: "Strings"
format: html
editor: visual
---

```{r}
alarm_report <-data.frame(
  stringsAsFactors = FALSE,
              date = c("2020-03-14", "2020-03-15", "2020-04-10", "2020-04-18"),
          building = c("Engineering-North",
                       "Bren Hall","Engineering-South","Engr-North"),
     alarm_message = c("10:02am – HVAC system down, facilities management alerted",
                       "8:24am – Elevator North out of service",
                       "12:41am – Fire alarm, UCSB fire responded and cleared",
                       "9:58pm – Campus point emergency siren, UCPD responded")
)
```

Practice working with strings by writing code to update alarm_report as follows (these can be separate, or all as part of a piped sequence):

-   Replace the "Engr" with "Engineering" in the building column
-   Separate the building column into two separate columns, building and wing, separated at the dash
-   Only keep observations with the word "responded" in the alarm_message column
-   Separate the message time from the rest of the message by separating at --
-   Convert the date column to a Date class using lubridate

```{r}
alarm_report_updated <- alarm_report %>%
  mutate(building = str_replace(building, pattern = "Engr", replacement = "Engineering")) %>%
  separate(building, c("building", "wing"), "-") %>%
  filter(str_detect(alarm_message, "responded")) %>%
  separate(alarm_message, c("time", "alarm_message"), " – ") %>%
  mutate(date = ymd(date),
         time = lubridate::hm(time)) %>%
  relocate(time, .after = date)

alarm_report_updated
```
